There exists a variety of attacks that exploit the vulnerabilities 
within networks and distributed applications. Some of these attacks
are able to deny clients from using a service (DoS, DDoS) while others
breach the internal system and extract confidential and private information \cite{mns}.
The implementation of network filtering as well as strong pod security policies can 
help mitigate these threats from causing harm to the service.

% Second para: describe the key problem that if solved would make
% an impact. Why the current approaches leave a gap?
Figuring out how to effectively utilize network filtering and
pod security policies to work together will hopefully result
in a strong security infrastructure that can successfully
defend against all attacks and will be adopted by all applications.

% Third: describe your approach. Key insight that enables your approach,
% and what is novel/interesting about the insight.
We will be researching how network filtering and pod security policies
function and how they can be applied to improving the security of
an application. By understanding how each work, we will be able to
understand how to effectively filter out network traffic that seems
suspicious, thus reducing the amount of potential attacks from the
start, and we will understand how to write a concrete and complete
pod security policy to defend against the attacks that slip through
the filter.

% Fourth, fifth: Delve deeper into the approach and experimental setup.
% In the final report, describe key findings.
Pod Security Policies (PSP) provides a framework that will layout the rules
of how a pod can operate and ensures that they run with the correct
privileges and access. Furthermore, PSPs are used so that those operating
Kubernetes clusters can control pod creations and limit what pods can access.
When a pod is deployed, the PSP acts as a gatekeeper that will compare the
pod security configuration to what is defined in the PSP. Some examples of how
PSPs can limit pod behaviors include, preventing privileged pods from starting
and controlling its privilege, restricting pods from accessing host namespaces,
filesystem, and networks, restrict the amount of user/groups that a pod can run,
and more.
Network filtering is the practice of monitoring the inflow/outflow of packets in
a network. There are two types of filtering, ingress and egress filtering.
Ingress filtering is the technique of monitoring incoming packet data.
It is considered the first-line of defense in a network because it blocks
out unwanted inflow traffic to the network. While this isn't a robust and complete
form of defense, it's beneficial because it can greatly reduce the load on some proxy
or firewall, and it's an effective for getting rid of the majority of unwanted traffic.
Egress filtering is the technique of monitoring the flow of outbound network traffic and
prevents any outbound connections to potential threats/unwanted hosts. Egress filtering
can be used to disrupt malware, block unwanted services, and gives greater awareness of
network traffic.
First, we will setup a simple application and document the vulnerabilities.
Next, we will implement pod security policies and document the results.
Then we will implement network filtering on the base application without pod security policies
and document the results. Finally, we will combine both layers of security and document the results.
Hopefully, the final application will be free of vulnerabilities.

% End with outline or what comes next and why.
Through our paper, we will show the effectiveness of and the need to implement robust Pod Security Policies
as well as a Network Proxy to aide with network filtering, in order to improve the overall security of a
distributed application. 
